Usage metrics

### 2020-12-07 inst/analysis/usage_metrics.Rmd
Eval calls per call site per un

knitr::opts_chunk$set(echo = TRUE,
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE,
                      time_it = TRUE)

@@

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "usage_metrics.tex"), prefix="", default=TRUE)
```

@@

```{r eval-calls-overview}
#own_eval_calls <- eval_calls %>% filter(eval_source == package) # probably to remove
own_eval_calls <- eval_calls
nb_eval_calls <- (own_eval_calls %>% count(wt = nb_ev_calls))$n

@@

```{r call-sites-violin-plot}
eval_calls %>% group_by(eval_source) %>% mutate(nb_call_sites = n_distinct(eval_call_srcref, na.rm = TRUE)) %>%
 ggplot(aes(x = eval_function, y = nb_call_sites, fill = eval_function), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  #geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y="Call sites per package") +
    theme(
    legend.position=c(0.5, 0.85),
    legend.box.background = element_rect(fill="white", size=0.1),
    legend.box="horizontal",
    axis.title.x=element_blank()
  )

@@

```{r nb-eval-calls}
# run = package?
eval_calls_per_package <- own_eval_calls %>% count(eval_source, wt=nb_ev_calls) %>% left_join(runs_package, by = "eval_source") %>% mutate(n = n / nb_runs)

@@

```{r eval-calls-violin-plot}
eval_calls_per_package %>%
 ggplot(aes(x = "", y = n, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  labs(y="Eval calls per package") +
  theme(
    legend.position= "none"
  )

@@

weighted.median <- function(x, w, na.rm=FALSE) {
  if(na.rm)
    na.omit(x)
  w <- w[order(x)]
  x <- x[order(x)]

  prob <- cumsum(w)/sum(w)
  ps <- which(abs(prob - .5) == min(abs(prob - .5)))
  return(x[ps])
}

@@

nb_nodes_many <- sizes_prop %>% filter(cumulative >= 0.95) %>% .[1,]

r("median size eval", med_size)
r("max size eval", max_size)
r("average size eval", average_size)
r("size nine five", nb_nodes_many$expr_expression_length)
r("size nine five exact percent", percent(nb_nodes_many$cumulative))

```

@@

```{r nb-events-violin-plot}
own_eval_calls %>% filter(direct_interpreter_eval > 0) %>%
 ggplot(aes(x = "", y = direct_interpreter_eval, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width=1.7)+
  scale_y_log10(labels = scales::comma) +
  labs(y="Number of events in eval per package") +
  theme(
    legend.position="none"
  )

@@

>>>>

knitr::opts_chunk$set(
  echo = TRUE,
  fig.retina = 2,
  fig.width = 10,
  cache.lazy = FALSE,
  time_it = TRUE
)

@@

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
create_tags(path(TAGS_DIR, "usage_metrics.tex"), prefix = "", default = TRUE)
```

@@

```{r eval-calls-overview}
# own_eval_calls <- eval_calls %>% filter(eval_source == package) # probably to remove
own_eval_calls <- eval_calls
nb_eval_calls <- (own_eval_calls %>% count(wt = nb_ev_calls))$n

@@

```{r call-sites-violin-plot}
eval_calls %>%
  group_by(eval_source) %>%
  mutate(nb_call_sites = n_distinct(eval_call_srcref, na.rm = TRUE)) %>%
  ggplot(aes(x = eval_function, y = nb_call_sites, fill = eval_function), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  # geom_jitter(shape=16, position=position_jitter(0.2)) +
  labs(y = "Call sites per package") +
  theme(
    legend.position = c(0.5, 0.85),
    legend.box.background = element_rect(fill = "white", size = 0.1),
    legend.box = "horizontal",
    axis.title.x = element_blank()
  )

@@

```{r nb-eval-calls}
# run = package?
eval_calls_per_package <- own_eval_calls %>%
  count(eval_source, wt = nb_ev_calls) %>%
  left_join(runs_package, by = "eval_source") %>%
  mutate(n = n / nb_runs)

@@

```{r eval-calls-violin-plot}
eval_calls_per_package %>%
  ggplot(aes(x = "", y = n, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  labs(y = "Eval calls per package") +
  theme(
    legend.position = "none"
  )

@@

weighted.median <- function(x, w, na.rm = FALSE) {
  if (na.rm) {
    na.omit(x)
  }
  w <- w[order(x)]
  x <- x[order(x)]

  prob <- cumsum(w) / sum(w)
  ps <- which(abs(prob - .5) == min(abs(prob - .5)))
  return(x[ps])
}

@@

nb_nodes_many <- sizes_prop %>%
  filter(cumulative >= 0.95) %>%
  .[1, ]

r("median size eval", med_size)
r("max size eval", max_size)
r("average size eval", average_size)
r("size nine five", nb_nodes_many$expr_expression_length)
r("size nine five exact percent", percent(nb_nodes_many$cumulative))
```

@@

```{r nb-events-violin-plot}
own_eval_calls %>%
  filter(direct_interpreter_eval > 0) %>%
  ggplot(aes(x = "", y = direct_interpreter_eval, fill = ""), na.rm = TRUE) +
  geom_violin(trim = FALSE, width = 1.7) +
  scale_y_log10(labels = scales::comma) +
  labs(y = "Number of events in eval per package") +
  theme(
    legend.position = "none"
  )

@@

# Loops

Here, we try to have an estimation of how often a call site is exercised per run. If it is often, maybe it is a loop!

```{r loops}
eval_calls_exercised <- eval_calls %>%
  group_by(file) %>%
  count(eval_call_srcref, wt = nb_ev_calls)

eval_calls_exercised %>% ggplot(aes(n)) +
  geom_histogram() +
  scale_x_log10(labels = scales::comma) +
  labs(x = "Number of eval calls per srcref per run")
```
